---
title: "Test 2"
output: html_document
date: "2022-10-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Load the Tidyverse and Patchwork libraries (5)
```{r}

```

2. Read in the mauna loa co2 file and the global temperature file. (5)
Be sure to check that they read in properly!
```{r}

```

3. Make a line plot of co2 concentrations over time from the Mauna Loa data. Be sure your plot has axis labels and looks good! (10)
```{r}

```

4. Make a plot of global temperature through time. Be sure this also conforms to good plot standards. (10)
```{r}

```

5. Filter the temperature records to the years matching those in the co2 dataset and make a plot of that filtered data. Use patchwork to create a composite plot with the co2 plot on the top and the temperature plot on the bottom. 

Remember, to do this, save each of your plots (ex: plot1 <- ggplot(...)) and then use mathematical symbols to tell patchwork how to combine them (+ for next to each other, / for on top) (15)
```{r}

```

6. Describe the trend in co2 and the trend in temperature. Do they appear to be related? (5)

7. Run the line of code below to create the plants dataset in your environment. 
Output a table with the mean uptake for each Type of plant for each Treatment. (10)

Info on these data: https://stat.ethz.ch/R-manual/R-devel/library/datasets/html/zCO2.html

```{r}
plants <- CO2

```

8. Create a new column in the plants dataset called efficiency. Make efficiency equal to the uptake divided by concentration multiplied by 100. (10)
```{r}

```

9. Output a table of the mean uptake and mean efficiency for each Type of plant for each Treatment. (10)
```{r}

```

10. Make a plot with concentration on the x axis and uptake on the y axis. Color the points by plant type and make the point shape depend on treatment. (10)
```{r}

```

11. Using evidence from BOTH number 10 plot and the number 9 table, describe the difference in how the Quebec and Mississippi plants responded to increasing co2 concentrations. (10) 
